\chapter{Conclusion}\label{ch:concl}
Today, donating to an organization or to any open collections seems like a very
difficult task. Since most of the fees are fraud or something like that. If we
describe this problem in more detail, we can make sure that if we wanted
to make a donation now, we would be faced with where to look for them. The second
question is that even if we find them, does he have any supporting documents that
will prove that the essence of the collection was really started for these purposes.
It is also necessary to take into account the issue of the payments themselves.
That is, in most cases these are simple transfers, from ordinary people to ordinary
people, which few people control on the side of collectors. And most of
the fees, one way or another, come through the vine, and also leads to various kinds of doubts.

And if we consider funds, the situation is a little rosy, because many
funds work in our country officially, and they create some fees from their names,
or they pay an open fee from their savings. You can read more in our research.
But, nevertheless, there are so many funds, and there is not much information about them
on the Internet, or they are not so media. And although they are official, many
bypass them, preferring to donate only to a few large, popular foundations. And
also, some open fees, even from popular funds, are opaque, that
is, there is no visual progress of the banal how much has been collected and how
much is left.

Just in such realities, our project cannot be replaced, since we have provided ideas for solving these problems. For example, by providing all fees to official funds, it was possible to avoid distrust of the collection. To solve the problem of shortcomings in fees, we provided online monitoring of each fee. We have implemented a quick money transfer functionality to reduce the time for donations. We have implemented the idea of checking documents and funds, so you can change your mind about fraud.

Charity work, despite the cultural, social, and economic crisis, is being implemented and will take an even broader framework in the future. And our solution will expand over time too. 

Everyone in need got help, and everyone who wanted to help could do it easily.